Optimal Decomposition-Recombination Plans for 2D Well-Constrained Graphs

### 2014-12-04 doc/GMP2015/s01_introduction.tex
s01_introduction.tex edited online with Bitbucket

Many natural and engineered materials are stacked two dimensional (2D) layers, where the structure within each layer is recursively 
self-similar \cite{Intro1}, 
spanning multiple scales. Within any one scale, the material layer is aperiodic, and quasi-uniform,
consisting of a few repeated motifs appearing in disordered arrangments.
Each layer is not necessarily planar, i.e., it consists of multiple, inter-constraining planar (genus 0) monolayers. 
Furthermore, a layer is often   either isostatic or somewhat flexible, and rarely self-stressed, at any scale. These properties are
consistent with a self-assembled 2D structure that minimizes mass, optimally distributes external stresses and itself 
participates in the assembly of diverse and multifunctional, 
larger 2D structures.

@@

In order to study structural and mechanical properties such as rigidity, flexes and distribution of external stresses 
within the material layer, 
it is natural to model them using appropriate geometric primitives under metric or algebraic constraints, 
Such  2D {\em sesamacs} (Self-similar, aperiodic material constraint systems) can be used to 
study robustness/sensitivity to constraint variations and to design material layers 
to achieve the desired properties.

Two key observations serve as the motivations for this paper:
As constraint systems, 2D sesamacs involve multiple types of 
well-studied geometric constraint systems: so-called
{\it bar-joint} systems (Examples 1,2 above), {\it multibody-pin} systems (Example 4,5) or {\it pinned-line incidence} systems (Example 3).  
All of these systems have highly efficient combinatorial algorithms (pebble-game \cite{XX}, or equivalently, simplified network flow \cite{XX}) 
for locating maximal, generically rigid components \cite{XX}.

Recursive decompositions of 2D sesamacs into rigid subsystems is important in order to understand or design rigidity, flexes and distribution 
of external stresses  -- at all scales.

>>>>

Many natural and engineered materials are stacked two dimensional (2D) layers, where the structure within each layer may be recursively 
self-similar \cite{Intro1}, 
spanning multiple scales. Within any one scale, the material layer is aperiodic, and quasi-uniform,
consisting of a few repeated motifs appearing in disordered arrangments.
Each layer is not necessarily planar, i.e., it consists of multiple, inter-constraining planar (genus 0) monolayers. 
Furthermore, a layer is often   either isostatic or somewhat flexible, and rarely self-stressed, at any scale. These properties are
consistent with a self-assembled 2D structure that minimizes mass, optimally distributes external stresses and itself 
participates in the assembly of diverse and multifunctional, 
larger 2D structures.

@@

In order to study structural and mechanical properties such as rigidity, flexes and distribution of external stresses 
within the material layer, it is natural to model a material layer as a solution of geometric constraint systems 
arising from appropriate geometric primitives under metric or algebraic constraints. 
Such  2D {\em sesamacs} (Self-similar or aperiodic material constraint systems) can be used to 
to understand or design material layers (their solutions) with desired properties.

As constraint systems, 2D sesamacs  are  well-studied: so-called
{\it bar-joint} systems (Examples 1,2 above), {\it multibody-pin} systems (Example 4,5) or {\it pinned-line incidence} systems (Example 3).  
All of these systems have highly efficient combinatorial algorithms (pebble-game \cite{XX}, or equivalently, simplified network flow \cite{XX}) 
for locating maximal, generically rigid subsystems \cite{XX}.

Whether self-similar, or just aperiodic, recursive decomposition of 2D sesamacs 
is imperative for understanding or designing rigidity, flexes and distribution 
of external stresses as well as robustness/sensitivity to constraint variations -- at all scales. 
In fact, the Decomposition-Recombination (DR)
-planning problem  for a geometric constraint system has been formalized \cite{XX} and 
studied by many \cite{XX}. The problem is purely combinatorial  - since decomposition does not require
knowledge of the geometry. In addition, there are efficient  algorithms 
for optimal recombination of solutions to child systems, in order to obtain a solution to the parent system at any
given level of the DR-plan.

In particular, since many different such decompositions typically exist, is to ensure 
that any system is decomposed into a minimal set 
of maximal rigid proper subsystems  
such that they can be recombined efficiently 
 Two key observations serve as the motivations for this paper:
